Understanding School Shootings: Analyzing Trends, Demographics, and Geographic Factors Using Bayesian Methods

### 2024-12-15 paper/paper.qmd
update the typo
update the typo

#### Loading the packages ####
library(tidyverse)
library(here)
library(maps)
library(ggplot2)
library(knitr)
library(brms)
library(bayesplot)
library(knitr)
library(kableExtra)
```

@@

#### Loading the dataset ####
data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
shooting_data <- data %>%
  filter(data_source == "raw")
non_shooting_data <-data %>%
  filter(data_source == "synthetic")
```

@@

To ensure the reliability of the Bayesian logistic regression model, the following diagnostics were conducted:
1. **Trace Plots:** @fig-trace-plots shows well-mixed chains for all parameters, confirming convergence.
2. **Rhat Plot:** @fig-rhat illustrates that all parameters have $\hat{R} \leq 1.1$, indicating no convergence issues.

@@

### C.1 Population, Frame, and Sample
- **Population:** All K-12 schools in the United States.
- **Frame:** Schools from the Washington Post dataset, combined with synthetic data for schools without shootings.
- **Sample:** Stratified by school type, urban locale description, and dominant demographic group.

### C.2 Sampling and Recruitment
- Synthetic data were generated within observed variable ranges to represent schools where shootings did not occur.
- Observed data were supplemented by demographic, geographic, and enrollment metrics.

### C.3 Questionnaire and Validation
- **Survey Focus:** School security measures, demographic composition, geographic details, and historical incidents.
- **Validation:** Cross-referenced data with administrative records to ensure accuracy.

@@

```
To simulate the occurrence of school shootings, synthetic data were generated with random variability:
- Geographic coordinates were adjusted within observed ranges.
- Demographics and enrollment were assigned proportionally based on observed distributions.

@fig-occurrence-map visualizes the geographic distribution of shooting occurrences, highlighting both observed and synthetic data points.
## E Implications of Results

@@

The analysis revealed the following key insights:
1. **Temporal Trends:** The increasing trend in shootings over time (@fig-trend) underscores the need for immediate interventions.

2. **Institutional and Demographic Context:** Public schools and urban locales were associated with higher risks, as shown in @fig-credible-intervals.
These findings provide actionable insights for policymakers aiming to mitigate risks associated with school shootings.

>>>>

#### Loading the packages ####
library(tidyverse)
library(here)
library(maps)
library(ggplot2)
library(knitr)
library(brms)
library(bayesplot)
library(knitr)
library(kableExtra)
library(arrow)
```

@@

library(arrow)

#### Loading the dataset ####
data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
shooting_data <- data %>%
  filter(data_source == "raw")
non_shooting_data <-data %>%
  filter(data_source == "synthetic")
```

@@

To ensure the reliability of the Bayesian logistic regression model, the following diagnostics were conducted:

1. **Trace Plots:** @fig-trace-plots shows well-mixed chains for all parameters, confirming convergence.

2. **Rhat Plot:** @fig-rhat illustrates that all parameters have $\hat{R} \leq 1.1$, indicating no convergence issues.

@@

### C.1 Population, Frame, and Sample
- **Population:** All K-12 schools in the United States.

- **Frame:** Schools from the Washington Post dataset, combined with synthetic data for schools without shootings.

- **Sample:** Stratified by school type, urban locale description, and dominant demographic group.

### C.2 Sampling and Recruitment
- Synthetic data were generated within observed variable ranges to represent schools where shootings did not occur.

- Observed data were supplemented by demographic, geographic, and enrollment metrics.

### C.3 Questionnaire and Validation
- **Survey Focus:** School security measures, demographic composition, geographic details, and historical incidents.

- **Validation:** Cross-referenced data with administrative records to ensure accuracy.

@@

```
To simulate the occurrence of school shootings, synthetic data were generated with random variability:

- Geographic coordinates were adjusted within observed ranges.

- Demographics and enrollment were assigned proportionally based on observed distributions.

@fig-occurrence-map visualizes the geographic distribution of shooting occurrences, highlighting both observed and synthetic data points.

## E Implications of Results

@@

```{r}
#| eval: true
#| echo: false
#| warning: false
#| label: fig-trend
#| fig-cap: "Tempotal Trend of School Shootings"

# Aggregate the number of shootings by year
trend_data <- shooting_data %>%
  group_by(year) %>%
  summarise(count = n())

# Create the temporal trend plot
ggplot(trend_data, aes(x = year, y = count)) +
  geom_line(color = "orange", size = 1) +
  geom_point(color = "orange", size = 2) +
  labs(
    x = "Year",
    y = "Number of Shootings"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

The analysis revealed the following key insights:

1. **Temporal Trends:** The increasing trend in shootings over time (@fig-trend) underscores the need for immediate interventions.

2. **Institutional and Demographic Context:** Public schools and urban locales were associated with higher risks, as shown in @fig-credible-intervals.

These findings provide actionable insights for policymakers aiming to mitigate risks associated with school shootings.
